### 2018-10-11 ANA-TOPQ-2017-07-PAPER-auxmat.tex
extra language editor comments

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htbp]
\small
\begin{center}
\begin{tabular}{l*{3}{c}}
\hline\hline
 & 4j, 2b & 4j, 3b & 4j, 4b \\
\hline
$\Hc$ & $ 1990 \pm 190 $ &   $ 1260 \pm 190 $ &   $ 24.8 \pm 9.5 $ \\
$\Hu$ & $ 1950 \pm 190 $ &   $ 1110 \pm 170 $ &   $ 19 \pm 16 $ \\ 
\hline
$\ttbar$+light-jets & $ 87000 \pm 11000 $ &   $ 4300 \pm 1200 $ &   $ 10.2 \pm 9.6 $ \\ 
$\ttcin$ & $ 8300 \pm 4300 $ &   $ 1050 \pm 640 $ &   $ 3.2 \pm 3.3 $ \\ 
$\ttbin$ & $ 3620 \pm 440 $ &   $ 2900 \pm 580 $ &   $ 95 \pm 33 $ \\ 
$t\bar{t}V$ & $ 176 \pm 31 $ &   $ 34.8 \pm 6.9 $ &   $ 2.84 \pm 0.74 $ \\ 
$t\bar{t}H$ & $ 61.7 \pm 9.2 $ &   $ 48.7 \pm 8.3 $ &   $ 5.1 \pm 1.0 $ \\
$W$+jets & $ 5400 \pm 2400 $ &   $ 280 \pm 130 $ &   $ 3.3 \pm 1.8 $ \\ 
$Z$+jets & $ 2120 \pm 960 $ &   $ 115 \pm 55 $ &   $ 2.4 \pm 1.4 $ \\ 
Single top & $ 7100 \pm 1300 $ &   $ 400 \pm 120 $ &   $ 7.8 \pm 6.0 $ \\ 
Diboson & $ 267 \pm 97 $ &   $ 17.2 \pm 6.5 $ &   $ 0.58 \pm 0.27 $ \\ 
Multijet & $ 7800 \pm 3400 $ &   $ 930 \pm 360 $ &   $ 31 \pm 17 $ \\
\hline
Total background & $ 120000 \pm 15000 $ &   $ 10000 \pm 2000 $ &   $ 162 \pm 44 $ \\ 
\hline
Data & 120572  & 11275  & 176  \\
\hline\hline    
\end{tabular}
%%\\
\vspace{0.2cm}

\begin{tabular}{l*{3}{c}}
\hline\hline
 & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
\hline
$\Hc$ & $ 1260 \pm 240 $ &   $ 1010 \pm 190 $ &   $ 26.2 \pm 8.8 $ \\ 
$\Hu$ & $ 1160 \pm 240 $ &   $ 930 \pm 160 $ &   $ 23 \pm 12 $ \\ 
\hline
$\ttbar$+light-jets & $ 41300 \pm 9100 $ &   $ 3200 \pm 900 $ &   $ 13 \pm 11 $ \\ 
$\ttcin$ & $ 5900 \pm 3100 $ &   $ 1320 \pm 760 $ &   $ 21 \pm 17 $ \\ 
$\ttbin$ & $ 3040 \pm 250 $ &   $ 4300 \pm 760 $ &   $ 310 \pm 83 $ \\ 
$t\bar{t}V$  &   $ 175 \pm 29 $ &   $ 67 \pm 12 $ &   $ 9.1 \pm 2.0 $ \\ 
$t\bar{t}H$  &   $ 81.3 \pm 9.5 $ &   $ 103 \pm 15 $ &   $ 18.4 \pm 3.5 $ \\ 
$W$+jets  &   $ 2400 \pm 1100 $ &   $ 186 \pm 89 $ &   $ 7.3 \pm 3.9 $ \\ 
$Z$+jets  &   $ 780 \pm 350 $ &   $ 83 \pm 39 $ &   $ 6.1 \pm 3.8 $ \\ 
Single top  &   $ 2990 \pm 780 $ &   $ 350 \pm 110 $ &   $ 16.6 \pm 7.6 $ \\ 
Diboson  &   $ 125 \pm 56 $ &   $ 13.7 \pm 6.3 $ &   $ 0.89 \pm 0.47 $ \\ 
Multijet  &   $ 3700 \pm 1500 $ &   $ 500 \pm 230 $ &   $ 3.8 \pm 4.9 $ \\ 
\hline
Total background &  $ 60000 \pm 11000 $ &   $ 10100 \pm 1900 $ &   $ 405 \pm 98 $ \\
\hline
Data & 58557  & 11707  & 466  \\ 
\hline\hline    
\end{tabular}
%%\\
\vspace{0.2cm}

\begin{tabular}{l*{3}{c}}
\hline\hline
 & $\geq$ 6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
\hline
$\Hc$ & $ 760 \pm 250 $ &   $ 690 \pm 210 $ &   $ 60 \pm 60 $ \\ 
$\Hu$ & $ 680 \pm 240 $ &   $ 570 \pm 180 $ &   $ 36 \pm 40 $ \\ 
\hline
$\ttbar$+light-jets  &   $ 22900 \pm 8100 $ &   $ 2400 \pm 910 $ &   $ 14 \pm 18 $ \\ 
$\ttcin$  &   $ 5300 \pm 3000 $ &   $ 1800 \pm 1100 $ &   $ 29 \pm 23 $ \\ 
$\ttbin$  &   $ 3270 \pm 510 $ &   $ 7300 \pm 1300 $ &   $ 1100 \pm 240 $ \\ 
$t\bar{t}V$  &   $ 229 \pm 41 $ &   $ 154 \pm 30 $ &   $ 30.8 \pm 6.9 $ \\ 
$t\bar{t}H$  &   $ 140 \pm 18 $ &   $ 262 \pm 39 $ &   $ 71 \pm 14 $ \\ 
$W$+jets  &   $ 1360 \pm 630 $ &   $ 200 \pm 100 $ &   $ 15.4 \pm 8.2 $ \\ 
$Z$+jets  &   $ 410 \pm 200 $ &   $ 63 \pm 32 $ &   $ 5.1 \pm 4.0 $ \\ 
Single top  &   $ 1510 \pm 560 $ &   $ 360 \pm 160 $ &   $ 34 \pm 20 $ \\ 
Diboson  &   $ 93 \pm 47 $ &   $ 18.5 \pm 9.6 $ &   $ 2.1 \pm 1.2 $ \\ 
Multijet  &   $ 1920 \pm 820 $ &   $ 780 \pm 360 $ &   $ 43 \pm 29 $ \\ 
\hline
Total background &  $ 37100 \pm 9600 $ &   $ 13400 \pm 2600 $ &   $ 1360 \pm 290 $ \\ 
\hline
Data & 35886  & 14877  & 1335  \\ 
\hline\hline    
\end{tabular}
%%\\
%\vspace{0.2cm}

%
\end{center}
%\vspace{-0.5cm}
\caption{
$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
The prediction is shown before the fit to data. Also shown are the signal expectations for 
$\Hc$ and $\Hu$ assuming $\BR(t\to Hc)=1\%$ and $\BR(t\to Hu)=1\%$ respectively.
The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
excluding the normalisation uncertainty of the $\ttbin$ background, which is determined via a likelihood fit to data.
}
\label{tab:Hbb_Prefit_Yields_Unblind}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htbp]
\small
\begin{center}
\begin{tabular}{l*{3}{c}}
\hline\hline
 & 4j, 2b & 4j, 3b & 4j, 4b \\
\hline
$\Hc$  &   $ -30 \pm 470 $ &   $ -20 \pm 300 $ &   $ -0.4 \pm 5.9 $ \\ 
\hline
$\ttbar$+light-jets  &    $ 82900 \pm 4200 $ &   $ 4900 \pm 500 $ &   $ 16 \pm 12 $ \\ 
$\ttcin$  &   $ 11400 \pm 4800 $ &   $ 1360 \pm 550 $ &   $ 5.9 \pm 4.2 $ \\ 
$\ttbin$  &   $ 4270 \pm 590 $ &   $ 3400 \pm 350 $ &   $ 110 \pm 17 $ \\ 
$t\bar{t}V$  &    $ 174 \pm 28 $ &   $ 35.0 \pm 5.9 $ &   $ 2.69 \pm 0.55 $ \\ 
$t\bar{t}H$  &   $ 62.6 \pm 7.8 $ &   $ 47.3 \pm 6.3 $ &   $ 4.68 \pm 0.69 $ \\ 
$W$+jets  &   $ 4800 \pm 1800 $ &   $ 260 \pm 100 $ &   $ 2.9 \pm 1.3 $ \\ 
$Z$+jets  &    $ 1870 \pm 730 $ &   $ 102 \pm 41 $ &   $ 1.9 \pm 1.0 $ \\ 
Single-top  &  $ 6360 \pm 980 $ &   $ 393 \pm 96 $ &   $ 7.6 \pm 5.2 $ \\ 
Diboson  &   $ 242 \pm 84 $ &   $ 16.3 \pm 5.7 $ &   $ 0.50 \pm 0.22 $ \\ 
Multijet  &   $ 9000 \pm 3500 $ &   $ 820 \pm 240 $ &   $ 29 \pm 16 $ \\ 
\hline
Total & $ 121100 \pm 2200 $ &   $ 11290 \pm 280 $ &   $ 181 \pm 23 $ \\ 
\hline
Data & 120572  & 11275  & 176  \\ 
\hline\hline      
\end{tabular}
%%\\
\vspace{0.2cm}

\begin{tabular}{l*{3}{c}}
\hline\hline
 & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
\hline
$\Hc$  &   $ -20 \pm 300 $ &   $ -10 \pm 240 $ &   $ -0.4 \pm 6.2 $ \\ 
\hline
$\ttbar$+light-jets  &   $ 38000 \pm 3100 $ &   $ 3480 \pm 460 $ &   $ 15.8 \pm 9.5 $ \\ 
$\ttcin$  &   $ 8300 \pm 3400 $ &   $ 2000 \pm 760 $ &   $ 39 \pm 18 $ \\ 
$\ttbin$  &   $ 3410 \pm 470 $ &   $ 4900 \pm 460 $ &   $ 356 \pm 29 $ \\ 
$t\bar{t}V$  &   $ 168 \pm 26 $ &   $ 65 \pm 10 $ &   $ 8.2 \pm 1.4 $ \\ 
$t\bar{t}H$  &   $ 81.1 \pm 8.9 $ &   $ 99 \pm 12 $ &   $ 16.6 \pm 2.3 $ \\ 
$W$+jets  &   $ 2080 \pm 820 $ &   $ 169 \pm 68 $ &   $ 6.0 \pm 2.8 $ \\ 
$Z$+jets  &   $ 700 \pm 270 $ &   $ 74 \pm 30 $ &   $ 5.6 \pm 3.2 $ \\ 
Single-top  &   $ 2560 \pm 590 $ &   $ 322 \pm 90 $ &   $ 13.3 \pm 5.8 $ \\ 
Diboson  &   $ 111 \pm 48 $ &   $ 12.5 \pm 5.4 $ &   $ 0.76 \pm 0.39 $ \\ 
Multijet  &   $ 3380 \pm 950 $ &   $ 560 \pm 230 $ &   $ 3.6 \pm 4.8 $ \\ 
\hline
Total & $ 58800 \pm 1400 $ &   $ 11690 \pm 360 $ &   $ 465 \pm 29 $ \\ 
\hline
Data & 58557  & 11707  & 466  \\ 
\hline\hline      
\end{tabular}
%%\\
\vspace{0.2cm}

\begin{tabular}{l*{3}{c}}
\hline\hline
 & $\geq$6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
\hline
$\Hc$  &   $ -10 \pm 180 $ &   $ -10 \pm 160 $ &   $ -1 \pm 14 $ \\ 
\hline
$\ttbar$+light-jets  &   $ 20100 \pm 2500 $ &   $ 2560 \pm 490 $ &   $ 21 \pm 23 $ \\ 
$\ttcin$  &   $ 7800 \pm 3300 $ &   $ 3000 \pm 1100 $ &   $ 59 \pm 25 $ \\ 
$\ttbin$  &   $ 3390 \pm 480 $ &   $ 7510 \pm 760 $ &   $ 1106 \pm 83 $ \\ 
$t\bar{t}V$  &   $ 213 \pm 34 $ &   $ 145 \pm 24 $ &   $ 27.0 \pm 4.8 $ \\ 
$t\bar{t}H$  &   $ 134 \pm 15 $ &   $ 240 \pm 30 $ &   $ 61.6 \pm 8.8 $ \\ 
$W$+jets  &   $ 1200 \pm 470 $ &   $ 183 \pm 75 $ &   $ 12.5 \pm 5.7 $ \\ 
$Z$+jets  &   $ 350 \pm 150 $ &   $ 56 \pm 24 $ &   $ 3.5 \pm 2.2 $ \\ 
Single-top  &   $ 1220 \pm 400 $ &   $ 310 \pm 120 $ &   $ 27 \pm 14 $ \\ 
Diboson  &   $ 82 \pm 40 $ &   $ 16.7 \pm 8.2 $ &   $ 1.70 \pm 0.90 $ \\ 
Multijet  &   $ 1540 \pm 530 $ &   $ 860 \pm 340 $ &   $ 37 \pm 26 $ \\ 
\hline
Total &   $ 36000 \pm 1300 $ &   $ 14880 \pm 500 $ &   $ 1360 \pm 72 $ \\ 
\hline
Data & 35886  & 14877  & 1335  \\
\hline\hline      
\end{tabular}
%%\\
%\vspace{0.2cm}

%
\end{center}
%\vspace{-0.5cm}
\caption{
$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
(assuming $\Hc$ as signal).
The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
computed taking into account correlations among nuisance parameters and among processes.
}
\label{tab:Hbb_Postfit_Yields_Unblind_Hc}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htbp]
\small
\begin{center}
\begin{tabular}{l*{3}{c}}
\hline\hline
 & 4j, 2b & 4j, 3b & 4j, 4b \\
\hline
$\Hu$  &   $ 40 \pm 550 $ &   $ 20 \pm 320 $ &   $ 0.4 \pm 5.3 $ \\
\hline
$\ttbar$+light-jets  &   $ 82700 \pm 4400 $ &   $ 4860 \pm 530 $ &   $ 15 \pm 12 $ \\ 
$\ttcin$  &   $ 11500 \pm 5100 $ &   $ 1400 \pm 580 $ &   $ 5.8 \pm 4.2 $ \\ 
$\ttbin$  &   $ 4260 \pm 590 $ &   $ 3400 \pm 350 $ &   $ 110 \pm 17 $ \\ 
$t\bar{t}V$  &   $ 173 \pm 28 $ &   $ 34.8 \pm 5.8 $ &   $ 2.68 \pm 0.54 $ \\ 
$t\bar{t}H$  &   $ 62.4 \pm 7.7 $ &   $ 47.1 \pm 6.2 $ &   $ 4.66 \pm 0.68 $ \\ 
$W$+jets  &   $ 4800 \pm 1900 $ &   $ 260 \pm 100 $ &   $ 2.9 \pm 1.4 $ \\ 
$Z$+jets  &   $ 1880 \pm 740 $ &   $ 103 \pm 42 $ &   $ 1.9 \pm 1.0 $ \\ 
Single-top  &   $ 6380 \pm 990 $ &   $ 392 \pm 96 $ &   $ 7.5 \pm 5.2 $ \\ 
Diboson  &   $ 243 \pm 85 $ &   $ 16.3 \pm 5.7 $ &   $ 0.50 \pm 0.22 $ \\ 
Multijet  &   $ 9000 \pm 3500 $ &   $ 810 \pm 240 $ &   $ 29 \pm 16 $ \\ 
\hline
Total &   $ 121000 \pm 2300 $ &   $ 11290 \pm 290 $ &   $ 181 \pm 23 $ \\ 
\hline
Data & 120572  & 11275  & 176  \\ 
\hline\hline      
\end{tabular}
%%\\
\vspace{0.2cm}

\begin{tabular}{l*{3}{c}}
\hline\hline
 & 5j, 2b & 5j, 3b & 5j, $\geq$4b \\
\hline
$\Hu$  &   $ 20 \pm 330 $ &   $ 20 \pm 270 $ &   $ 0.4 \pm 6.6 $ \\ 
\hline
$\ttbar$+light-jets  &   $ 37800 \pm 3400 $ &   $ 3450 \pm 500 $ &   $ 15.8 \pm 9.7 $ \\ 
$\ttcin$  &   $ 8400 \pm 3700 $ &   $ 2000 \pm 800 $ &   $ 39 \pm 19 $ \\ 
$\ttbin$  &   $ 3400 \pm 470 $ &   $ 4920 \pm 460 $ &   $ 356 \pm 29 $ \\ 
$t\bar{t}V$  &   $ 168 \pm 26 $ &   $ 65 \pm 10 $ &   $ 8.2 \pm 1.4 $ \\ 
$t\bar{t}H$  &   $ 81.0 \pm 8.9 $ &   $ 99 \pm 12 $ &   $ 16.6 \pm 2.3 $ \\ 
$W$+jets  &   $ 2100 \pm 840 $ &   $ 169 \pm 69 $ &   $ 6.0 \pm 2.8 $ \\ 
$Z$+jets  &   $ 710 \pm 280 $ &   $ 74 \pm 30 $ &   $ 5.5 \pm 3.2 $ \\ 
Single-top  &   $ 2570 \pm 600 $ &   $ 320 \pm 90 $ &   $ 13.4 \pm 5.8 $ \\ 
Diboson  &   $ 112 \pm 48 $ &   $ 12.5 \pm 5.5 $ &   $ 0.77 \pm 0.39 $ \\ 
Multijet  &   $ 3430 \pm 990 $ &   $ 560 \pm 230 $ &   $ 3.6 \pm 4.8 $ \\ 
\hline
Total &   $ 58800 \pm 1500 $ &   $ 11690 \pm 380 $ &   $ 465 \pm 29 $ \\ 
\hline
Data & 58557  & 11707  & 466  \\ 
\hline\hline      
\end{tabular}
%%\\
\vspace{0.2cm}

\begin{tabular}{l*{3}{c}}
\hline\hline
 & $\geq$6j, 2b & $\geq$6j, 3b & $\geq$6j, $\geq$4b \\
\hline
$\Hu$ &   $ 10 \pm 190 $ &   $ 10 \pm 160 $ &   $ 1 \pm 10 $ \\ 
\hline
$\ttbar$+light-jets  &   $ 20000 \pm 2700 $ &   $ 2530 \pm 520 $ &   $ 20 \pm 24 $ \\ 
$\ttcin$  &   $ 7900 \pm 3600 $ &   $ 3000 \pm 1200 $ &   $ 58 \pm 26 $ \\ 
$\ttbin$  &   $ 3390 \pm 480 $ &   $ 7520 \pm 760 $ &   $ 1106 \pm 83 $ \\ 
$t\bar{t}V$  &   $ 213 \pm 34 $ &   $ 147 \pm 24 $ &   $ 27.0 \pm 4.8 $ \\ 
$t\bar{t}H$  &   $ 135 \pm 16 $ &   $ 241 \pm 30 $ &   $ 61.9 \pm 9.0 $ \\ 
$W$+jets  &   $ 1210 \pm 480 $ &   $ 184 \pm 76 $ &   $ 12.6 \pm 5.8 $ \\ 
$Z$+jets  &   $ 360 \pm 150 $ &   $ 57 \pm 24 $ &   $ 3.6 \pm 2.2 $ \\ 
Single-top  &   $ 1240 \pm 400 $ &   $ 320 \pm 120 $ &   $ 27 \pm 14 $ \\ 
Diboson  &   $ 83 \pm 40 $ &   $ 16.8 \pm 8.3 $ &   $ 1.71 \pm 0.91 $ \\ 
Multijet  &   $ 1530 \pm 530 $ &   $ 860 \pm 340 $ &   $ 37 \pm 26 $ \\ 
\hline
Total &   $ 36000 \pm 1400 $ &   $ 14880 \pm 530 $ &   $ 1360 \pm 73 $ \\ 
\hline
Data & 35886  & 14877  & 1335  \\
\hline\hline      
\end{tabular}
%%\\
%\vspace{0.2cm}

%
\end{center}
%\vspace{-0.5cm}
\caption{
$\Hbb$ search: Predicted and observed yields in each of the analysis regions considered.
The background prediction is shown after the fit to data under the signal-plus-background hypothesis (assuming $\Hu$ as signal).
The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
computed taking into account correlations among nuisance parameters and among processes.
}
\label{tab:Hbb_Postfit_Yields_Unblind_Hu}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htbp]
\small
\begin{center}
\begin{tabular}{l*{4}{c}}
\hline\hline
 & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
\hline
$\Hc$  &   $ 89 \pm 14 $ &   $ 226 \pm 43 $ &   $ 46 \pm 14 $ &   $ 122 \pm 32 $ \\ 
$\Hu$  &   $ 100 \pm 17 $ &   $ 237 \pm 47 $ &   $ 32 \pm 10 $ &   $ 114 \pm 28 $ \\ 
\hline
Fake $\had$  &   $ 2828 \pm 78 $ &   $ 3200 \pm 100 $ &   $ 710 \pm 110 $ &   $ 500 \pm 62 $ \\
Top (real $\had$)  &   $ 3840 \pm 720 $ &   $ 3160 \pm 890 $ &   $ 113 \pm 72 $ &   $ 117 \pm 35 $ \\  
$Z \to \tau\tau$  &   $ 420 \pm 140 $ &   $ 320 \pm 120 $ &   $ 283 \pm 99 $ &   $ 267 \pm 96 $ \\ 
Other  &   $ 168 \pm 56 $ &   $ 103 \pm 33 $ &   $ 8.9 \pm 2.5 $ &   $ 11.2 \pm 2.5 $ \\ 
\hline
Total background  &   $ 7260 \pm 730 $ &   $ 6770 \pm 880 $ &   $ 1120 \pm 120 $ &   $ 900 \pm 120 $ \\ 
\hline
Data  & 7259  & 6768  & 1119  & 894  \\
\hline\hline    
\end{tabular}
%%\\
%\vspace{0.2cm}

%
\end{center}
%\vspace{-0.5cm}
\caption{
$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
The prediction is shown before the fit to data. Also shown are the signal expectations for 
$\Hc$ and $\Hu$ assuming $\BR(t\to Hc)=1\%$ and $\BR(t\to Hu)=1\%$ respectively.
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
excluding the normalisation uncertainty of the fake $\had$ background, which is determined via a likelihood fit to data.
}
\label{tab:Htautau_Prefit_Yields_Unblind}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htbp]
\small
\begin{center}
\begin{tabular}{l*{4}{c}}
\hline\hline
 & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
\hline
$\Hc$  &   $ -4.2 \pm 8.2 $ &   $ -11 \pm 21 $ &   $ -2.4 \pm 4.3 $ &   $ -10 \pm 11 $ \\ 
\hline
Fake $\had$  &   $ 2290 \pm 680 $ &   $ 2640 \pm 880 $ &   $ 640 \pm 110 $ &   $ 440 \pm 100 $ \\ 
Top (real $\had$)  &   $ 4300 \pm 670 $ &   $ 3660 \pm 860 $ &   $ 147 \pm 84 $ &   $ 139 \pm 35 $ \\ 
$Z \to \tau\tau$  &   $ 500 \pm 100 $ &   $ 359 \pm 90 $ &   $ 320 \pm 79 $ &   $ 306 \pm 76 $ \\ 
Other  &   $ 178 \pm 45 $ &   $ 112 \pm 28 $ &   $ 9.6 \pm 2.6 $ &   $ 12.5 \pm 2.6 $ \\ 
\hline
Total  &   $ 7230 \pm 160 $ &   $ 6760 \pm 170 $ &   $ 1117 \pm 65 $ &   $ 893 \pm 45 $ \\
\hline
Data & 7259  & 6768  & 1119  & 894 \\ 
\hline\hline    
\end{tabular}
%%\\
%\vspace{0.2cm}

%
\end{center}
%\vspace{-0.5cm}
\caption{
$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
(assuming $\Hc$ as signal).
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
computed taking into account correlations among nuisance parameters and among processes.
}
\label{tab:Htautau_Postfit_Yields_Unblind_Hc}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[htbp]
\small
\begin{center}
\begin{tabular}{l*{4}{c}}
\hline\hline
 & $\lephad$ 3j & $\lephad$ $\geq$4j & $\hadhad$ 3j &  $\hadhad$ $\geq$4j \\
\hline
$\Hu$  &   $ -5.7 \pm 8.6 $ &   $ -14 \pm 21 $ &   $ -2,0 \pm 2.8 $ &   $ -7.1 \pm 9.8 $ \\ 
\hline
Fake $\had$  &   $ 2270 \pm 680 $ &   $ 2620 \pm 880 $ &   $ 640 \pm 110 $ &   $ 440 \pm 100 $ \\
Top (real $\had$)  &   $ 4320 \pm 660 $ &   $ 3680 \pm 860 $ &   $ 148 \pm 84 $ &   $ 140 \pm 35 $ \\ 
$Z \to \tau\tau$  &   $ 470 \pm 100 $ &   $ 359 \pm 89 $ &   $ 321 \pm 79 $ &   $ 308 \pm 77 $ \\ 
Other  &   $ 177 \pm 44 $ &   $ 111 \pm 27 $ &   $ 9.7 \pm 2.6 $ &   $ 12.5 \pm 2.6 $ \\ 
\hline
Total  &   $ 7230 \pm 160 $ &   $ 6760 \pm 160 $ &   $ 1118 \pm 66 $ &   $ 892 \pm 45 $ \\ 
\hline
Data  & 7259  & 6768  & 1119  & 894  \\ 
\hline\hline    
\end{tabular}
%%\\
%\vspace{0.2cm}

%
\end{center}
%\vspace{-0.5cm}
\caption{
$\Htautau$ search: Predicted and observed yields in each of the analysis regions considered.
The background prediction is shown after the fit to data under the signal-plus-background hypothesis 
(assuming $\Hu$ as signal).
The contributions with real $\had$ candidates from $\ttbar$,  $\ttbar V$, $\ttbar H$, and single-top-quark backgrounds are combined into
a single background source referred to as ``Top (real $\had$)'', whereas the small contributions from 
$Z\to \ell^+\ell^-$ ($\ell = e, \mu$) and diboson backgrounds are combined into ``Other''. 
The quoted uncertainties are the sum in quadrature of statistical and systematic uncertainties of the yields, 
computed taking into account correlations among nuisance parameters and among processes.
}
\label{tab:Htautau_Postfit_Yields_Unblind_Hu}
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-10-11 sections/objects.tex
extra language editor comments

Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\had$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
Any $\had$ candidate that is also $b$-tagged is rejected.

@@

Overlaps between reconstructed objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
and muon candidates are removed. Clusters from identified electrons are not excluded during jet reconstruction. 
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
The overlap removal procedure in the $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
first step is the removal of $\had$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\had$ candidates (depending on the
analysis channel). In addition, the muon--jet overlap removal is slightly different:
if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 
primary vertex or it has a small $\pt$ compared to that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
or the scalar sum of the $\pt$ of the tracks associated to the jet is less than 70\% of the $\pt$ of the muon).

>>>>

Hadronically decaying $\tau$-lepton ($\had$) candidates are reconstructed from energy clusters in the calorimeters and
associated inner detector tracks~\cite{ATL-PHYS-PUB-2015-045}. Candidates are required to have either one or three associated tracks,
with a total charge of $\pm 1$. Candidates are required to have $\pt > 25~\gev$ and $|\eta|<2.5$, excluding the EM calorimeter's transition region.
A boosted decision tree (BDT) discriminant~\cite{Breiman:1984jka,Friedman:2002we,Freund:1997xna} using calorimeter- and tracking-based variables is used to identify $\had$ candidates and reject
jet backgrounds. Three working points labelled loose, medium and tight are defined, and correspond to different $\had$ identification efficiency 
values, with the efficiency designed to be independent of $\pt$. The $\Htautau$ search uses the medium
working point for the nominal selection, while the loose working point is used for background estimation.
The medium working point has a combined reconstruction and identification efficiency of 55\% (40\%) for one (three)-prong $\had$ 
decays~\cite{ATLAS-CONF-2017-029}, and an expected rejection factor against light-jets of 100~\cite{ATL-PHYS-PUB-2015-045}. 
Electrons that are reconstructed as one-prong $\had$ candidates are removed via a BDT trained to reject electrons.
Any $\had$ candidate that is also $b$-tagged is rejected.

@@

Overlaps between reconstructed objects are removed sequentially. In the $\Hbb$ search, firstly, electron candidates that lie 
within $\Delta R = 0.01$ of a muon candidate are removed to suppress contributions from muon bremsstrahlung. 
Overlaps between electron and jet candidates are resolved next, and finally, overlaps between remaining jet candidates 
and muon candidates are removed. Energy clusters from identified electrons are not excluded during jet reconstruction. 
In order to avoid double-counting of electrons as jets, the closest jet whose axis is within ${\Delta}R = 0.2$ of an electron 
is discarded. If the electron is within ${\Delta}R = 0.4$ of the axis of any jet after this initial removal, the jet is retained and  the electron is removed.
The overlap removal procedure between the remaining jet candidates and muon candidates is designed to remove those muons 
that are likely to have arisen in the decay of hadrons and to retain the overlapping jet instead. 
Jets and muons may also appear in close proximity when the jet results from high-$\pt$ muon bremsstrahlung, 
and in such cases the jet should be removed and the muon retained. Such jets are characterised by having very 
few matching inner-detector tracks. Selected muons that satisfy $\Delta R(\mu,{\textrm{jet}}) < 0.04+10~\gev/\pt^\mu$ are rejected
if the jet has at least three tracks originating from the primary vertex; otherwise the jet is removed and the muon is kept.
The overlap removal procedure in the $\Htautau$ search is similar to that of the $\Hbb$ search, except that the
first step is the removal of $\had$ candidates within $\Delta R=0.2$ of electrons or muons, and the last step is the
removal of jets whose axis lies within $\Delta R=0.2$ of the highest-$\pt$ (leading) or the two leading $\had$ candidates (depending on the
analysis channel). In addition, the muon--jet overlap removal is slightly different:
if a muon lies within $\Delta R = 0.2$ of the axis of a jet, the jet is removed if either it has fewer than three tracks originating from the 
primary vertex or it has a small $\pt$ compared to that of the muon (the $\pt$ of the jet is less than 50\% of the $\pt$ of the muon,
or the scalar sum of the $\pt$ of the tracks associated to the jet is less than 70\% of the $\pt$ of the muon).
